\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-09 k-planar.tex
Updated analysis of layered width

  \note{PM}{Pick up here tomorrow afternoon. For now I have to teach and prepare a talk.}
  The proof finishes in the same way as the proof in \cite{DJMMUW20}.  The paths $P_1,\ldots,P_k$, and $S=V(Y^+)$ become elements of the $H$-partition.
  Elements in each of the $H$-partitions of $N_1,\ldots,N_m$ that intersect $P_1,\ldots,P_k$, or $V(\overline{Y}^+-F)$ are discarded and all the resulting sets are combined to obtain an $H$-partition of $G$.

@@

	Let $G'$ be the plane graph obtained by removing one spar from each kite of $\overline{G}$ and let $T$ be a BFS tree of $G'$ rooted at $r$.  Now apply \cref{induction} with $G=\overline{G}$, $G'$, $F$, and $P_i=\{v_i\}$ for each $i\in\{1,2,3\}$.  This gives an $H$-partition $\{S_x:x\in V(H)\}$ of $\overline{G}-\{r\}\supseteq G$ in which $H$ is planar and has treewidth at most 3.

	Use the layering $\mathcal{L}=\langle L_0',L_1'\ldots\rangle$ where $L_i'=L_{2i}\cup L_{2i+1}$ for each integer $i\ge 0$. That this is a layering of $G$ follows from the fact that $\dist_{G'}(v,w)\le 2$ for every edge $vw\in E(G)$.  Since $|L_j\cap S_x|\le 15$ for every integer $j\ge 0$, $|L_i'\cap S_x|\le 30$ for every integer $i\ge 0$ and every $x\in V(H)$. The result follows from \cref{PartitionProduct}.
\end{proof}

>>>>

  \note{PM}{Pick up here tomorrow, after teaching.}
  The proof finishes in the same way as the proof in \cite{DJMMUW20}.  The paths $P_1,\ldots,P_k$, and $S=V(Y^+)$ become elements of the $H$-partition.
  Elements in each of the $H$-partitions of $N_1,\ldots,N_m$ that intersect $P_1,\ldots,P_k$, or $V(\overline{Y}^+-F)$ are discarded and all the resulting sets are combined to obtain an $H$-partition of $G$.

@@

	Let $G'$ be the plane graph obtained by removing both spars from each kite of $\overline{G}$ and let $T$ be a BFS tree of $G'$ rooted at $r$.  Now apply \cref{induction} with $G=\overline{G}$, $G'$, $F$, and $P_i=\{v_i\}$ for each $i\in\{1,2,3\}$.  This gives an $H$-partition $\{S_x\cup\{v_x\}:x\in V(H)\}$ of $\overline{G}-\{r\}\supseteq G$ in which $H$ is planar and has treewidth at most 3.

	Use the layering $\mathcal{L}=\langle L_0',L_1'\ldots\rangle$ where $L_i'=L_{2i}\cup L_{2i+1}$ for each integer $i\ge 0$. That this is a layering of $G$ follows from the fact that $\dist_{G'}(v,w)\le 2$ for every edge $vw\in E(G)$.  Since $|L_j\cap S_x|\le 3$ for every integer $j\ge 0$, $|L_i'\cap (S_x\cup\{v_x\})|\le 7$ for every integer $i\ge 0$ and every $x\in V(H)$. The result follows from \cref{PartitionProduct}.
\end{proof}
